A standardized framework for risk-based assessment of treatment effect heterogeneity in observational healthcare databases

### 2021-08-31 submission/manuscript.rmd
separate evaluation from results in methods section
rewrite presentation of results

## Step 5: Evaluation and presentation of results

@@

In the presence of a positive treatment effect and a well-discriminating
prediction model we expect an increasing pattern of the differences in the
absolute scale, even if treatment effects remain constant on the relative scale
across risk strata. Results should be presented side-by-side on a
forest-plot-like format, so that the evolution of treatment effects across risk
strata is visible both on the relative and the absolute scale.

>>>>

## Step 5: Evaluation

@@

## Step 6: Presentation of results

In the presence of a positive treatment effect and a well-discriminating
prediction model we expect an increasing pattern of the differences in the
absolute scale, even if treatment effects remain constant on the relative scale
across risk strata. Due to this scale-dependence of treatment effect
heterogeneity, results should be assessed both on the relative and the absolute
scale. We find that a side-by-side presentation on a forest-like format can give
a very good representation of our results.
